---
title: "Atmospheric Conductance - Sensitivity Analysis"
author: "Group L: Genevieve Chiong, Peter Menzies, Alex Clippinger"
date: '`r format(Sys.time(), "%m/%d/%Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pse)
library(tidyverse)

source("compute_atmospheric_conductance.R")
```


# Parts 1-2. Create and Run Atmospheric Conductance Model

The following model is sourced from "compute_atmospheric_conductance.R".

```{r single_estimate}
compute_atmospheric_conductance()
```

The model's single estimate of atmospheric conductance (for a forest that is 10 m high, has wind speeds of 250 cm/s, and a wind speed measurement height (cm) of 200 cm above vegetation) is 15.44228 cm/s.


# Part 3. Sensitivity Analysis

Vegetation height is assumed to be randomly distributed between 9.5 and 10.5 m. The k_d and k_0 parameters are assumed to be normally distributed with standard deviation of 1% of their default values. Wind speeds are normally distributed with a mean of 250 cm/s and standard deviation of 30 cm/s.


### a. Use LHS to generate parameter values for the 4 parameters

```{r lhs}
factors = c("vegetation_ht", "k_d", "k_0", "wind_speed")

nsets = 100

q = c("qunif", # vegetation height randomly distributed
      "qnorm", # k_d normally distributed
      "qnorm",
      "qnorm"
      )

q.arg = list(list(min = 950, max = 1050), # vegetation height
             list(mean = 0.7, sd = 0.7*0.01), 
             list(mean = 0.1, sd = 0.1*0.01),
             list(mean = 250, sd = 30))

set.seed(1001)
sens_conductance = LHS(NULL, factors, nsets, q, q.arg)
sens_pars = get.data(sens_conductance)
head(sens_pars)
```


### b. Run atmospheric conductance model for these parameter sets

```{r parameter_uncertainty}
conductances = sens_pars %>% pmap(compute_atmospheric_conductance)

conductances_df = conductances %>% map_dfr(`[`, c("conductance"))

sens_conductance = pse::tell(sens_conductance, t(as.matrix(conductances_df)),
                             res.names = c("conductance"))
```


### c. Plot conductance estimates accounting for parameter uncertainty

Conductance estimates, accounting for parameter uncertainty, are displayed using a boxplot and histogram below. 

```{r conductance_boxplot}
ggplot(conductances_df, aes(y=conductance)) +
  geom_boxplot() +
  theme_light() +
  labs(title = "Distribution of Conductance Estimates Given Parameter Uncertainty")
```

```{r conductance_hist, warning=FALSE}
ggplot(conductances_df, aes(conductance)) +
  geom_histogram() +
  theme_light() +
  labs(title = "Distribution of Conductance Estimates Given Parameter Uncertainty")
```


### d. Plot conductance estimates against each parameter

```{r conductance_scatter}
pse::plotscatter(sens_conductance)
```

The plots above indicate that there is a stronger relationship between wind speed uncertainty and conductance than that of the other three parameters.


### e. Estimate the Partial Rank Correlation Coefficients (PRCC)

The PRCC values are plotted and displayed below.

```{r prcc_plot}
pse::plotprcc(sens_conductance)
```

```{r prcc_values}
sens_conductance$prcc
```

Additionally, Spearman correlation for these four values are given below.

```{r spearman}
veg_cor = cor(conductances_df$conductance, sens_pars$vegetation_ht, method = "spearman")
kd_cor = cor(conductances_df$conductance, sens_pars$k_d, method = "spearman")
k0_cor = cor(conductances_df$conductance, sens_pars$k_0, method = "spearman")
windspd_cor = cor(conductances_df$conductance, sens_pars$wind_speed, method = "spearman")

parameters = c("Vegetation Height", "k_d", "k_0", "Wind Speed")
cors = c(veg_cor, kd_cor, k0_cor, windspd_cor)

tibble("Parameter" = parameters,
       "Correlation" = cors)
```


### f. Discussion of Results

The results of our sensitivity analysis on atmospheric conductance indicate that conductance is most heavily impacted by uncertainty in wind speed. The other parameters - vegetation height, k_0, and k_d, are less impactful given uncertainty. This suggests that in order to reduce uncertainty in aerodynamic conductance estimates, the most important parameter to control for is wind speed. 

Given this observation, climate change may exacerbate plant water use sensitivity if warmer climate results in higher wind speed conditions. 

